---
title: "Clean Data CA"
author: "Halina Do-Linh"
date: "1/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# attached packages
library(tidyverse)
library(janitor)
library(here)
```

# Read in yearly reservation datasets

```{r}
ridb_2020 <- read_csv(here("../../data_raw/FY20-historical-reservations-full.csv"))
ridb_2019 <- read_csv(here("../../data_raw/reservations2019.csv"))
ridb_2018 <- read_csv(here("../../data_raw/reservations2018.csv"))
# ridb_2017 <- read_csv(here("data", "2017.csv"))
# ridb_2016 <- read_csv(here("data", "2016.csv"))
# ridb_2015 <- read_csv(here("data", "2015.csv"))
# ridb_2014 <- read_csv(here("data", "2014.csv"))
# ridb_2013 <- read_csv(here("data", "2013.csv"))
# ridb_2012 <- read_csv(here("data", "2012.csv"))
# ridb_2011 <- read_csv(here("data", "2011.csv"))
# ridb_2010 <- read_csv(here("data", "2010.csv"))
```

# Tidy variables for 2019 year

```{r}
select_columns <- c("historicalreservationid",
         "ordernumber",
         "agency",
         "orgid",
         "regioncode", "regiondescription",
         "parentlocationid", "parentlocation",
         "sitetype", "usetype",
         "productid", 
         "inventorytype", 
         "facilityid", "facilityzip", "facilitystate", "facilitylongitude", "facilitylatitude",
         "customerzip", 
         "totalbeforetax", "discount", "totalpaid",
         "startdate", "enddate", "orderdate",
         "numberofpeople")

rm_sitetype <- c("historic tour",
                 "hiking zone",
                 "group picnic area",
                 "cave tour",
                 "management",
                 "anchorage",
                 "picnic",
                 "entry point",
                 "trailhead")
```


# Tidy variables for 2018-2010 years

```{r}
# inventory_type and discount columns don't exist

select_columns_18 <- c("historical_reservation_id",
         "order_number",
         "agency",
         "org_id",
         "region_code", "region_description",
         "parent_location_id", "parent_location",
         "site_type", "use_type",
         "product_id", 
         "facility_id", "facility_zip", "facility_state", "facility_longitude", "facility_latitude",
         "customer_zip", 
         "total_before_tax", "total_paid",
         "start_date", "end_date", "order_date",
         "number_of_people")
```

# Tidy 2010 Data

```{r}
# column names with underscores
ridb_2010_clean <- ridb_2010 %>% 
  janitor::clean_names() %>% 
  select(select_columns_18) %>% 
  filter(facility_state == "CA") %>% 
  mutate(site_type = tolower(site_type)) %>% 
  filter(site_type != rm_sitetype) %>% 
  filter(use_type == "Overnight") %>%
  filter(customer_zip == str_extract_all(customer_zip,"[[:digit:]]{5}"))
```

# Tidy 2011 Data

```{r}
# column names with underscores
ridb_2011_clean <- ridb_2011 %>% 
  janitor::clean_names() %>% 
  select(select_columns_18) %>% 
  filter(facility_state == "CA") %>% 
  mutate(site_type = tolower(site_type)) %>% 
  filter(site_type != rm_sitetype) %>% 
  filter(use_type == "Overnight") %>%
  filter(customer_zip == str_extract_all(customer_zip,"[[:digit:]]{5}"))
```

# Tidy 2012 Data

```{r}
# column names with underscores
ridb_2012_clean <- ridb_2012 %>% 
  janitor::clean_names() %>% 
  select(select_columns_18) %>% 
  filter(facility_state == "CA") %>% 
  mutate(site_type = tolower(site_type)) %>% 
  filter(site_type != rm_sitetype) %>% 
  filter(use_type == "Overnight") %>%
  filter(customer_zip == str_extract_all(customer_zip,"[[:digit:]]{5}"))
```

# Tidy 2013 Data

```{r}
# column names with underscores
ridb_2013_clean <- ridb_2013 %>% 
  janitor::clean_names() %>% 
  select(select_columns_18) %>% 
  filter(facility_state == "CA") %>% 
  mutate(site_type = tolower(site_type)) %>% 
  filter(site_type != rm_sitetype) %>% 
  filter(use_type == "Overnight") %>%
  filter(customer_zip == str_extract_all(customer_zip,"[[:digit:]]{5}"))
```

# Tidy 2014 Data

```{r}
# column names with underscores
ridb_2014_clean <- ridb_2014 %>% 
  janitor::clean_names() %>% 
  select(select_columns_18) %>% 
  filter(facility_state == "CA") %>% 
  mutate(site_type = tolower(site_type)) %>% 
  filter(site_type != rm_sitetype) %>% 
  filter(use_type == "Overnight") %>%
  filter(customer_zip == str_extract_all(customer_zip,"[[:digit:]]{5}"))
```


# Tidy 2015 Data

```{r}
# column names with underscores
ridb_2015_clean <- ridb_2015 %>% 
  janitor::clean_names() %>% 
  select(select_columns_18) %>% 
  filter(facility_state == "CA") %>% 
  mutate(site_type = tolower(site_type)) %>% 
  filter(site_type != rm_sitetype) %>% 
  filter(use_type == "Overnight") %>%
  filter(customer_zip == str_extract_all(customer_zip,"[[:digit:]]{5}"))
```

# Tidy 2016 Data

```{r}
# column names with underscores
ridb_2016_clean <- ridb_2016 %>% 
  janitor::clean_names() %>% 
  select(select_columns_18) %>% 
  filter(facility_state == "CA") %>% 
  mutate(site_type = tolower(site_type)) %>% 
  filter(site_type != rm_sitetype) %>% 
  filter(use_type == "Overnight") %>%
  filter(customer_zip == str_extract_all(customer_zip,"[[:digit:]]{5}"))
```

# Tidy 2017 Data

```{r}
# column names with underscores
ridb_2017_clean <- ridb_2017 %>% 
  janitor::clean_names() %>% 
  select(select_columns_18) %>% 
  filter(facility_state == "CA") %>% 
  mutate(site_type = tolower(site_type)) %>% 
  filter(site_type != rm_sitetype) %>% 
  filter(use_type == "Overnight") %>%
  filter(customer_zip == str_extract_all(customer_zip,"[[:digit:]]{5}"))
```

# Tidy 2018 Data

```{r}
# column names with underscores
ridb_2018_clean <- ridb_2018 %>% 
  janitor::clean_names() %>% 
  select(select_columns_18) %>% 
  filter(facility_state == "CA") %>% 
  mutate(site_type = tolower(site_type)) %>% 
  filter(site_type != rm_sitetype) %>% 
  filter(use_type == "Overnight") %>%
  filter(customer_zip == str_extract_all(customer_zip,"[[:digit:]]{5}"))
```


# Tidy 2019 Data

```{r}
ridb_2019_clean <- ridb_2019 %>% 
  janitor::clean_names() %>% 
  select(select_columns) %>% 
  filter(facilitystate == "California") %>% 
  mutate(sitetype = tolower(sitetype)) %>% 
  filter(sitetype != rm_sitetype) %>% 
  filter(usetype == "Overnight") %>%
  filter(customerzip == str_extract_all(customerzip,"[[:digit:]]{5}"))
```

- 2019 ridb clean had to remove `nights` column does not exist

# Tidy 2020 Data (OG Cleaning)

```{r}
ridb_2020_clean <- ridb_2020 %>% 
  janitor::clean_names() %>% 
  select("historicalreservationid",
         "ordernumber",
         "agency",
         "orgid",
         "regioncode", "regiondescription",
         "parentlocationid", "parentlocation",
         "sitetype", "usetype",
         "productid", "inventorytype", 
         "facilityid", "facilityzip", "facilitystate", "facilitylongitude", "facilitylatitude",
         "customerzip", 
         "totalbeforetax",
         "discount", "totalpaid",
         "startdate", "enddate", "orderdate",
         "nights",
         "numberofpeople") %>% 
  filter(facilitystate == "California") %>% 
  mutate(sitetype = tolower(sitetype)) %>% 
  filter(sitetype != c("historic tour",
                      "hiking zone",
                      "group picnic area",
                      "cave tour",
                      "management",
                      "anchorage",
                      "picnic",
                      "entry point",
                      "trailhead")) %>% 
  filter(usetype == "Overnight") %>% 
  mutate(nights = gsub(" days", "", nights)) %>% # used tidyverse gsub to remove day and days
  mutate(nights = as.numeric(gsub(" day", "", nights))) %>% # make the column numeric instead of chr
  filter(customerzip == str_extract_all(customerzip,"[[:digit:]]{5}"))

```

# Other cleaning functions

- used `get_dupes()` to confirm that there are no duplicate rows within `historicalreservationid`
- 2020 clean data has no dupes!
- 2019 clean data has potentially 299,247 dupes...
- 2018 clean data has potentially 17,749 dupes...

```{r}
ridb_2019_dupes <- ridb_2019 %>% 
  filter(historicalreservationid == "000103ba-6b5a-5a30-a17e-0bf8ada0dbdf")
```


```{r}
  ridb_2019_clean <- ridb_2019 %>% 
    # filter for state
    filter(facilitystate == "California") %>%
    # select variables
    select(c("historicalreservationid",
             "agency",
             "parentlocation",
             "park",
             "sitetype", 
             "usetype",
             "facilitystate", 
             "facilitylongitude", 
             "facilitylatitude",
             "customerzip", 
             "totalpaid",
             "startdate",
             "enddate", 
             "orderdate",
             "numberofpeople")) %>% 
    mutate(sitetype = tolower(sitetype)) %>% 
    filter(!sitetype %in% c("historic tour",
                             "hiking zone",
                             "group picnic area",
                             "cave tour",
                             "management",
                             "anchorage",
                             "picnic",
                             "entry point",
                             "trailhead")) %>% 
    filter(usetype == "Overnight") %>%
    # filter out invalid ZIP codes
    filter(customerzip == str_extract_all(customerzip, "[[:digit:]]{5}")) %>% 
    # remove use type column
    select(!usetype)

```


```{r}
janitor::get_dupes(ridb_2019_clean, historicalreservationid)
```


```{r}
  ridb_2018_clean <- ridb_2018 %>% 
    clean_names() %>% 
    # filter for state
    filter(facility_state == "CA") %>%
    # select variables
    select(c("historical_reservation_id",
             "agency",
             "parent_location",
             "park",
             "site_type", 
             "use_type",
             "facility_state", 
             "facility_longitude", 
             "facility_latitude",
             "customer_zip", 
             "total_paid",
             "start_date",
             "end_date", 
             "order_date",
             "number_of_people")) %>% 
    mutate(site_type = tolower(site_type)) %>% 
    filter(!site_type %in% c("historic tour",
                             "hiking zone",
                             "group picnic area",
                             "cave tour",
                             "management",
                             "anchorage",
                             "picnic",
                             "entry point",
                             "trailhead")) %>% 
    filter(use_type == "Overnight") %>%
    # filter out invalid ZIP codes
    filter(customer_zip == str_extract_all(customer_zip, "[[:digit:]]{5}")) %>% 
    # remove use type column
    select(!use_type)

```


```{r}
ridb_2018_dupes <- ridb_2018_clean %>% 
  filter(historical_reservation_id == "2474865457")
  
```


```{r}
dupes_2018 <- janitor::get_dupes(ridb_2018_clean, historical_reservation_id) %>% group_by(historical_reservation_id, dupe_count)
```



# At this point:

- `sitetype`: 
"standard nonelectric"
"group walk to"                   
"walk to"                         
"group standard area nonelectric"  
"group standard nonelectric"      
"tent only nonelectric"            
"group tent only area nonelectric"
”group shelter nonelectric"       
"rv nonelectric"                                        
"tent only electric"                                       
"standard electric"                
"cabin nonelectric"               
"group equestrian"                 
"boat in"                         
"group hike to"                    
"hike to"                         
"rv electric"                      
"cabin electric"                  
"equestrian nonelectric"          
"group standard electric"          
"group standard area electric"    
"yurt"                            
"group rv area nonelectric"        
"shelter nonelectric"
- `sitetype` removed: "group shelter electric", "destination zone", NAs
- `usetype` is only "Overnight"
- `inventorytype` is only "CAMPING"
- `nights` is numeric and removed " day" and " days". When changed to numeric NAs were introduced by coercion. I think this came up because there were some 00:00:00 values and these can't numeric.
- `startdate`, `enddate`, `orderdate` classes are "POSIXct" or "POSIXt" 
- `customerzip` now only contains zip codes with 5 digit numbers; class is character

# Cleaning for data 2018-2010:

- because of how the raw column names are we are getting two versions of clean names: one with and one without underscores.
- `facility_state` is not "California" (which it is for 2019 and 2020); datasets 2018-2010 use "CA". We should ask which convention will be used moving forward...
- just from the number of rows/ observations you can see that there is an obvious increasing trend in number of reservations over time.

