---
title: "Data Cleaning"
author: "Clarissa Boyajian and Halina Do-Linh"
date: "1/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)
library(lubridate)
library(scales)
library(vroom)
library(sf)
library(tidycensus)
library(zipcodeR)
library(tmap)
library(tigris)
library(rmapshaper)
library(googlesheets4) # read in metadata sheets

options(scipen = 999)

# RIDB functions
# data subset
source("functions/function_ridb_subset-pre2018.R")
source("functions/function_ridb_subset-post2019.R")
# clean data and calculate variables
source("functions/function_ridb_variable_calculate-pre2018.R")

# ACS functions
source("functions/function_acs_race.R")
source("functions/function_acs_median_income.R")
source("functions/function_acs_education.R")
source("functions/function_acs_language.R")

# join RIDB and ACS function
source("functions/function_join_ridb_acs.R")

# state and ZIP code geometries functions
source("functions/function_map_ca_data.R")
source("functions/function_map_us_data.R")

# ACS variable top quantile and decile functions
source("functions/function_acs_deciles_median_income.R")
source("functions/function_acs_top_quartile_education.R")
source("functions/function_acs_top_quartile_language.R")
source("functions/function_acs_top_quartile_race.R")

# RIDB df above ACS "high" threshold functions
source("functions/function_ridb_top_quartile_education.R")
source("functions/function_ridb_top_quartile_language.R")
source("functions/function_ridb_top_quartile_race.R")
source("functions/function_ridb_deciles_median_income.R")
```

# RIDB - read in data, calculate varibales, standardize values

```{r}
## 2018 CA
# read in data subset for specific year and state 
data_ridb_2018_subset <- RIDB_subset_pre2018(full_file_path = "../../data_raw/reservations2018.csv", 
                                      state_abbrev = "CA", year = 2018)
# clean and calculate variables
data_ridb_2018_clean <- RIDB_calculate_pre2018(input_df_name = data_ridb_2018_subset)
```

```{r, eval = FALSE}
# check all agency, admin_unit, and park strings look correct
# check there are no duplicate parks at different admin units
admin_unit_park_check <- data_ridb_2018_clean %>% 
  select(agency, admin_unit, park) %>% 
  unique() %>% 
  relocate(park, .before = 1) %>% 
  arrange(park)
View(admin_unit_park_check)
```



# Census Data - API set up, read, subset, calculate values

```{r, message=FALSE}
# API set up

# # ONLY HAVE TO RUN THE FIRST TIME USING THIS RMD on a new machine
# census_api <- source("private/census-api.R")
# census_api_key(key = census_api[[1]], install = TRUE, overwrite = TRUE)
# # run in console:
## readRenviron("~/.Renviron")

# look at option variables
#View(load_variables(2018, "acs5", cache = TRUE))
```

```{r}
# read in, subset, and clean census data for all US ZIP codes
acs_subset_calculate_race(geography = "zcta", year = 2018, state = NULL)
acs_subset_calculate_median_income(geography = "zcta", year = 2018, state = NULL)
acs_subset_calculate_education(geography = "zcta", year = 2018, state = NULL)
acs_subset_calculate_language(geography = "zcta", state = NULL)
```


# Join RIDB and Census dataframes

```{r}
data_combined_2018 <- join_ridb_acs_data(ridb_df = data_ridb_2018_clean,
                                         acs_df_race = data_acs_2018_race_percent,
                                         acs_df_education = data_acs_2018_education_percent,
                                         acs_df_median_income = data_acs_2018_median_income,
                                         acs_df_language = data_acs_2020_language_percent)
```




# Create dataframe for full CA census

```{r}
# read in census data for CA
acs_subset_calculate_race(geography = "zcta", year = 2018, state = "California")
acs_subset_calculate_education(geography = "zcta", year = 2018, state = "California")
acs_subset_calculate_language(geography = "zcta", state = "California")
acs_subset_calculate_median_income(geography = "zcta", year = 2018, state = "California")

# combine all CA census variables
acs_ca_all <- left_join(x = data_acs_2018_education_percent_California,
                     y = data_acs_2018_median_income_California,
                     by = "zip_code") %>% 
  left_join(y = data_acs_2018_race_percent_California,
            by = "zip_code") %>% 
  left_join(y = data_acs_2020_language_percent_California,
            by = "zip_code")

data_acs_ca_all <- acs_ca_all %>% 
  mutate(mean_zip_code_population = rowMeans(acs_ca_all[,c(2,8,17)])) %>% 
  select(-c("zip_code_population.x", 
            "zip_code_population.y",
            "zip_code_population"))
```


# Create dataframes of all reservations above "high" threshhold values for each ACS variables

```{r}
## -- education -- ##
education_group <-
  c("hs_GED_or_below", "some_college",  "college", "master_or_above")

# calculate value of 3rd quartile for each educational group
education_quants_df <-
  education_group %>%
  map_dbl(education_top_quartile, acs_df = data_acs_ca_all) %>%
  cbind("education_group" = education_group,
        "weighted_quartile" = .) %>%
  as.data.frame()

# create dataframe of all reservations above threshold
data_education_above_threshold <-
  education_quants_df %>% pmap_dfr(education_ridb_top_quartile,
                                   joined_ridb_acs_df = data_combined_2018)
```


```{r}
## -- language -- ##
language_group <- c("english_only", "not_english_only")

# calculate value of 3rd quartile for each language group
language_quants_df <-
  language_group %>%
  map_dbl(language_top_quartile, acs_df = data_acs_ca_all) %>%
  cbind("language_group" = language_group,
        "weighted_quartile" = .) %>%
  as.data.frame()

# create dataframe of all reservations above threshold
data_language_above_threshold <-
  language_quants_df %>% pmap_dfr(language_ridb_top_quartile,
                                  joined_ridb_acs_df = data_combined_2018)
```


```{r}
## -- median-income -- ##

# calculate decile values
median_income_decile_list <-
  median_income_deciles(acs_df = data_acs_ca_all) %>%
  as.list()

# create dataframe of all reservations split into deciles
data_median_income_deciles <- median_income_ridb_deciles(median_income_binned = median_income_decile_list,
                                                         joined_ridb_acs_df = data_combined_2018)
```


```{r}
## -- race -- ##
race_group <- c(
  "other", "pacific_islander",  "multiracial",  "asian",
  "black",  "white", "native_american", "hispanic_latinx")

# calculate value of 3rd quartile for each racial group
race_quants_df <-
  race_group %>%
  map_dbl(race_top_quartile, acs_df = data_acs_ca_all) %>%
  cbind("race_group" = race_group,
        "weighted_quartile" = .) %>%
  as.data.frame()

# create dataframe of all reservations above threshold
data_race_above_threshold <-
  race_quants_df %>% pmap_dfr(race_ridb_top_quartile,
                              joined_ridb_acs_df = data_combined_2018)
```




# Create dataframes for visitorshed maps

```{r}
ca_zip_geometries <- zip_ca_dataframe(state = "California", year = 2018)

state_geometries <- state_geometries_dataframe(year = 2018)
```

# Create dataframe for CA city labels on visitorshed map

```{r}
ca_city_labels <- 
  # get geometries for CA cities
  urban_areas(cb = TRUE) %>% 
  select(NAME10, geometry) %>% 
  rename(city = NAME10) %>% 
  # separate city and state strings
  separate(col= city, into = c("city", "state"), sep = ", ") %>% 
  # filter to only CA cities
  filter(state == "CA") %>% 
  mutate(city = str_replace(string = city,
                            pattern = "-.*$",
                            replacement = "")) %>% 
  # calculate center point of each polygon geometry
  st_centroid() %>% 
  select(city, geometry) %>% 
  # filter to only major CA cities
  filter(city %in% c("Bakersfield", "Fresno", "Los Angeles", "Mount Shasta", 
                     "Redding", "Sacramento", "San Diego", "Santa Barbara", 
                     "San Francisco", "San Jose")) %>%
  st_transform(crs = 4269) # using NAD83 because measured in meters
```


# Create metadata dataframe

```{r}
# get metadata csv and create csv in r
data_joined_2018_metadata <- 
  googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19ZQiaTlSoo1-KlPibeIoVbo0IT0ZU2soFa0XGAEHF88/edit?usp=sharing")
```



# Saving dataframes

## Save to CSV

```{r}
# full dataset (RIDB and ACS joined)
write.csv(x = data_combined_2018, 
          file = "../../../data_clean/2018_joined_data.csv", 
          row.names = FALSE)

# all acs vars joined
write.csv(x = data_acs_ca_all,
          "../../../data_clean/2018_ca_acs_all.csv",
          row.names = FALSE)

# metadata
write_csv(data_joined_2018_metadata,
          file = here("outdoor-equity-app/oe_app/data/data_joined_2018_metadata.csv"))
```

## Save to RDS

```{r}
# bootstrap geometries and reproject to NAD83
data_combined_2018_geometry <- 
  data_combined_2018 %>% 
  st_as_sf(coords = c("facility_latitude", "facility_longitude"),
           crs = 4326) %>% 
  st_transform(crs = 4269) # using NAD83 because measured in meters


## -- save RDS files to `data` directory within Shiny App directories -- ##

# full dataset (RIDB and ACS joined) with geometries
saveRDS(object = data_combined_2018_geometry,
        file = "outdoor-equity-app/oe_app/data/2018_joined_data_geometries.rds")

# full dataset (RIDB and ACS joined) without geometries
saveRDS(object = data_combined_2018,
        file = "outdoor-equity-app/oe_app/data/2018_joined_data.rds")

# all acs variables joined
saveRDS(object = data_acs_ca_all,
        file = "outdoor-equity-app/oe_app/data/2018_ca_acs_all.rds")

# education data for relationship plots
saveRDS(object = data_education_above_threshold,
        file = "../shiny/outdoor-equity-app/oe_app/data/education_relationship_plots.rds")

# language data for relationship plots
saveRDS(object = data_language_above_threshold,
        file = "../shiny/outdoor-equity-app/oe_app/data/language_relationship_plots.rds")

# median-income data for relationship plots
saveRDS(object = data_median_income_deciles,
        file = "outdoor-equity-app/oe_app/data/median_income_relationship_plots.rds")

# race data for relationship plots
saveRDS(object = data_race_above_threshold,
        file = ".outdoor-equity-app/oe_app/data/race_relationship_plots.rds")

# CA zip code geometries
saveRDS(object = ca_zip_geometries,
        file = "../shiny/outdoor-equity-app/oe_app/data/ca_zip_codes_geometries.rds")

# state geometries
saveRDS(object = state_geometries,
        file = "../shiny/outdoor-equity-app/oe_app/data/states_geometries.rds")

# CA city label geometries
saveRDS(object = ca_city_labels,
        file = "outdoor-equity-app/oe_app/data/ca_cities_geometries.rds")
```



