---
title: "Data Viz for Shiny App"
author: "Clarissa"
date: "3/17/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

library(tidyverse)
library(here)
library(janitor)
library(lubridate)
library(sf)
library(tidycensus)
library(patchwork)
library(scales)
library(tmap)
library(vroom)
library(paletteer)

options(scipen = 999)

# load script to pull and clean ACS data
source("../functions/function_acs_race.R")
source("../functions/function_acs_median_income.R")
source("../functions/function_acs_transportation.R")
source("../functions/function_acs_education.R")
source("../functions/function_acs_language.R")
```


```{r load data, message=FALSE}
# read in joined data
data_ridb_acs_2018 <- vroom(file = "../../../../data_clean/2018_joined_data.csv",
                            delim = ",") ## non-map graphs (no geometries)
# data_ridb_acs_2018 <- readRDS(file = "../../../../data_clean/2018_joined_data.rds") ## maps (don't use RDS for non-map viz, too slow)

# ACS CA data
acs_subset_calculate_race(geography = "zcta", year = 2018, state = "California")
acs_subset_calculate_education(geography = "zcta", year = 2018, state = "California")
acs_subset_calculate_language(geography = "zcta", state = "California")
acs_subset_calculate_transportation(geography = "zcta", year = 2018, state = "California")
acs_subset_calculate_median_income(geography = "zcta", year = 2018, state = "California")

# ACS US data
# acs_subset_calculate_race(geography = "zcta", year = 2018, state = NULL)
# acs_subset_calculate_education(geography = "zcta", year = 2018, state = NULL)
```


## Agency Analysis: Comparison Graphs

#### Race x distance traveled (Option 1)

```{r}
## -- data wrangle -- ##
data_plot_race_distance_traveled_bins <- data_ridb_acs_2018 %>% 
  select(agency, regional_area, park, customer_zip, asian, black, hispanic_latinx, 
         multiracial, native_american, other, pacific_islander, white,
         distance_traveled_m) %>% 
  mutate(distance_traveled_mi = distance_traveled_m * 0.000621371) %>% 
  drop_na(distance_traveled_mi) %>% 
  mutate(distance_traveled_bins = ntile(distance_traveled_mi, 5)) 

data_plot_race_distance_traveled <- data_plot_race_distance_traveled_bins %>% 
  group_by(distance_traveled_bins) %>% 
  summarize(white = (mean(white, na.rm = TRUE) * 100),
            black = (mean(black, na.rm = TRUE) * 100),
            asian = (mean(asian, na.rm = TRUE) * 100),
            multiracial = (mean(multiracial, na.rm = TRUE) * 100),
            other = (mean(other, na.rm = TRUE) * 100),
            native_american = (mean(native_american, na.rm = TRUE) * 100),
            pacific_islander = (mean(pacific_islander, na.rm = TRUE) * 100),
            hispanic_latinx = (mean(hispanic_latinx, na.rm = TRUE) * 100)) %>% 
  pivot_longer(cols = 2:9,
               names_to = "race",
               values_to = "race_percentage") %>% 
  mutate(race = str_replace(string = race,
                            pattern = "_",
                            replacement = " "),
         race = str_to_title(race))
  
distance_traveled_bin_breaks <- quantile(data_plot_race_distance_traveled_bins$distance_traveled_mi, 
                                         prob = seq(0, 1, length = 6), type = 5)
         

## -- create plot -- ##

# parameters
racial_group_colors <- c("Other" = "#999999", "Pacific Islander" = "#E69F00", "Multiracial" = "#56B4E9",
                              "Asian" = "#009E73", "Black" = "#F0E442", "White" = "#0072B2", 
                              "Native American" = "#D55E00", "Hispanic Latinx" = "#CC79A7")

# plot for shiny
plot_race_distance_traveled <- ggplot(data = data_plot_race_distance_traveled) +
  geom_col(aes(x = factor(distance_traveled_bins),
               y = race_percentage,
               fill = reorder(race, race_percentage)),
           stat = "identity",
           position = "dodge") +
  coord_flip() +
  scale_fill_manual(values = racial_group_colors) +
  scale_x_discrete(labels = c("1" = "0 - 60.2", "2" = "60.2 - 116.9", "3" = "116.9 - 180.9", 
                              "4" = "180.9 - 299.3", "5" = "299.3 - \n3,613.7"), 
                   breaks = c("1", "2", "3", "4", "5")) +
  geom_vline(xintercept = c(0.5, 1.5, 2.5, 3.5, 4.5), 
             color = "lightgrey") +
  labs(x = "Distance Traveled (miles)",
       y = "Percentage (%)",
       title = "Breakdown of Race of Home ZIP Codes vs. Distance Traveled",
       subtitle = "for Overnight Reservations in California",
       fill = "Race") +
  theme_minimal() +
  theme(plot.background = element_rect("white"),
        panel.grid.major.x = element_blank()
        # ## only needed for saving as image
        # axis.text = element_text(size = 20),
        # axis.title = element_text(size = 22, face = "bold"),
        # title = element_text(size = 24, face = "bold")
        )
plot_race_distance_traveled
```

#### Race x distance traveled (Option 2)

```{r}
ggplot(data = data_plot_race_distance_traveled) +
  geom_col(aes(x = factor(distance_traveled_bins),
               y = race_percentage,
               fill = race),
           stat = "identity",
           position = "dodge") +
  facet_wrap(~race, scales = "free_x") +
  scale_fill_manual(values = racial_group_colors) +
  scale_x_discrete(labels = c("1" = "0 - 60.2 miles", "2" = "60.2 - 116.9 miles", "3" = "116.9 - 180.9 miles", 
                              "4" = "180.9 - 299.3 miles", "5" = "299.3 - 3,613.7 miles"), 
                   breaks = c("1", "2", "3", "4", "5")) +
  coord_flip() +
  labs(x = "Distance Traveled (miles)",
       y = "Percentage (%)",
       title = "Breakdown of Race of Home ZIP Codes vs. Distance Traveled",
       subtitle = "for Overnight Reservations in California") +
  theme(legend.position = "none")
```


#### Race x distance traveled (Option 3)

```{r}
# data
test <- data_plot_race_distance_traveled_bins %>% 
  select(asian, black, hispanic_latinx, multiracial, native_american, 
         other, pacific_islander, white, distance_traveled_bins) %>% 
  pivot_longer(cols = 1:8,
               names_to = "race",
               values_to = "race_percentage") %>% 
  mutate(race = str_replace(string = race,
                            pattern = "_",
                            replacement = " "),
         race = str_to_title(race))

# plot
ggplot(data = test) +
  geom_boxplot(aes(x = factor(distance_traveled_bins),
                   y = race_percentage, 
                   fill = race),
               varwidth = TRUE, outlier.shape = NA) +
  coord_flip() +
  facet_wrap(~race, scales = "free_x") +
  scale_fill_manual(values = racial_group_colors) +
  scale_x_discrete(labels = c("1" = "0 - 60.2 miles", "2" = "60.2 - 116.9 miles", "3" = "116.9 - 180.9 miles",
                              "4" = "180.9 - 299.3 miles", "5" = "299.3 - 3,613.7 miles"),
                   breaks = c("1", "2", "3", "4", "5")) +
  coord_flip() +
  labs(x = "Distance Traveled (miles)",
       y = "Percentage (%)",
       title = "Breakdown of Race of Home ZIP Codes vs. Distance Traveled",
       subtitle = "for Overnight Reservations in California") +
  theme(legend.position = "none")
```



#### Race x site type (Option 1)

```{r}
## -- data wrangle -- ##
data_plot_race_site_type <- data_ridb_acs_2018 %>% 
  select(agency, regional_area, park, customer_zip, asian, black, hispanic_latinx, 
         multiracial, native_american, other, pacific_islander, white,
         aggregated_site_type) %>% 
  group_by(aggregated_site_type) %>% 
  summarize(white = (mean(white, na.rm = TRUE) * 100),
            black = (mean(black, na.rm = TRUE) * 100),
            asian = (mean(asian, na.rm = TRUE) * 100),
            multiracial = (mean(multiracial, na.rm = TRUE) * 100),
            other = (mean(other, na.rm = TRUE) * 100),
            native_american = (mean(native_american, na.rm = TRUE) * 100),
            pacific_islander = (mean(pacific_islander, na.rm = TRUE) * 100),
            hispanic_latinx = (mean(hispanic_latinx, na.rm = TRUE) * 100)) %>% 
  pivot_longer(cols = 2:9,
               names_to = "race",
               values_to = "race_percentage") %>% 
  mutate(race = str_replace(string = race,
                            pattern = "_",
                            replacement = " "),
         race = str_to_title(race))
         

## -- create plot -- ##

# parameters
racial_group_colors <- c("Other" = "#999999", "Pacific Islander" = "#E69F00", "Multiracial" = "#56B4E9",
                              "Asian" = "#009E73", "Black" = "#F0E442", "White" = "#0072B2", 
                              "Native American" = "#D55E00", "Hispanic Latinx" = "#CC79A7")

# plot for shiny
plot_race_site_type <- ggplot(data = data_plot_race_site_type) +
  geom_col(aes(x = aggregated_site_type,
               y = race_percentage,
               fill = reorder(race, race_percentage)),
           stat = "identity",
           position = "dodge") +
  coord_flip() +
  scale_fill_manual(values = racial_group_colors) +
  geom_vline(xintercept = c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5, 6.5), 
             color = "lightgrey") +
  scale_x_discrete(limits = c("equestrian", "remote", "rv only", "rv or tent", "shelter", "tent only", "water"),
                   labels = c("Equestrian", "Remote", "RV Only", "RV or Tent", "Shelter", "Tent Only", "Water")) +
  labs(x = "Site Types",
       y = "Percentage (%)",
       fill = "Race",
       title = "Breakdown of Race of Home ZIP Codes vs. Site Type",
       subtitle = "for Overnight Reservations in California") +
  theme_minimal() +
  theme(plot.background = element_rect("white"),
        panel.grid.major.x = element_blank()
        # ## only needed for saving as image
        # axis.text = element_text(size = 20),
        # axis.title = element_text(size = 22, face = "bold"),
        # title = element_text(size = 24, face = "bold")
        )
plot_race_site_type
```

#### Race x site type (Option 2)

```{r}

```


#### Race x booking window (Option 1)

```{r}
## -- data wrangle -- ##
data_plot_race_booking_window_bins <- data_ridb_acs_2018 %>% 
  select(agency, regional_area, park, customer_zip, asian, black, hispanic_latinx, 
         multiracial, native_american, other, pacific_islander, white,
         booking_window) %>% 
  filter(booking_window >= 0) %>%
  mutate(booking_window_bins = ntile(booking_window, 5)) 

data_plot_race_booking_window <- data_plot_race_booking_window_bins %>% 
  group_by(booking_window_bins) %>% 
  summarize(white = (mean(white, na.rm = TRUE) * 100),
            black = (mean(black, na.rm = TRUE) * 100),
            asian = (mean(asian, na.rm = TRUE) * 100),
            multiracial = (mean(multiracial, na.rm = TRUE) * 100),
            other = (mean(other, na.rm = TRUE) * 100),
            native_american = (mean(native_american, na.rm = TRUE) * 100),
            pacific_islander = (mean(pacific_islander, na.rm = TRUE) * 100),
            hispanic_latinx = (mean(hispanic_latinx, na.rm = TRUE) * 100)) %>% 
  pivot_longer(cols = 2:9,
               names_to = "race",
               values_to = "race_percentage") %>% 
  mutate(race = str_replace(string = race,
                            pattern = "_",
                            replacement = " "),
         race = str_to_title(race))
  
booking_window_bin_breaks <- quantile(data_plot_race_booking_window_bins$booking_window, 
                                      prob = seq(0, 1, length = 6), type = 5)
         

## -- create plot -- ##

# parameters
racial_group_colors <- c("Other" = "#999999", "Pacific Islander" = "#E69F00", "Multiracial" = "#56B4E9",
                              "Asian" = "#009E73", "Black" = "#F0E442", "White" = "#0072B2", 
                              "Native American" = "#D55E00", "Hispanic Latinx" = "#CC79A7")

# plot for shiny
plot_race_booking_window <- ggplot(data = data_plot_race_booking_window) +
  geom_col(aes(x = factor(booking_window_bins),
               y = race_percentage,
               fill = reorder(race, race_percentage)),
           stat = "identity",
           position = "dodge") +
  coord_flip() +
  scale_fill_manual(values = racial_group_colors) +
  scale_x_discrete(labels = c("1" = "0 - 7 \n(days)", "2" = "7 - 27 \n(days)", 
                              "3" = "1 - 2.5 \n(months)", "4" = "2.5 - 4.5 \n(months)", 
                              "5" = "4.5 months - \n1.8 years"), 
                   breaks = c("1", "2", "3", "4", "5")) +
  geom_vline(xintercept = c(0.5, 1.5, 2.5, 3.5, 4.5), 
             color = "lightgrey") +
  labs(x = "Booking window",
       y = "Percentage (%)",
       title = "Breakdown of Race of Home ZIP Codes vs. Booking Window",
       subtitle = "for Overnight Reservations in California",
       fill = "Race") +
  theme_minimal() +
  theme(plot.background = element_rect("white"),
        panel.grid.major.x = element_blank()
        # ## only needed for saving as image
        # axis.text = element_text(size = 20),
        # axis.title = element_text(size = 22, face = "bold"),
        # title = element_text(size = 24, face = "bold")
        )

plot_race_booking_window
```

#### Race x booking window (Option 2)

```{r}

```


#### Race x daily cost (Option 1)

```{r}
## -- data wrangle -- ##
data_plot_race_daily_cost_bins <- data_ridb_acs_2018 %>% 
  select(agency, regional_area, park, customer_zip, asian, black, hispanic_latinx, 
         multiracial, native_american, other, pacific_islander, white,
         daily_cost_per_visitor) %>% 
  filter(daily_cost_per_visitor >= 0,
         daily_cost_per_visitor != "Inf") %>%
  mutate(daily_cost_per_visitor_bins = ntile(daily_cost_per_visitor, 5)) 

data_plot_race_daily_cost <- data_plot_race_daily_cost_bins %>% 
  group_by(daily_cost_per_visitor_bins) %>% 
  summarize(white = (mean(white, na.rm = TRUE) * 100),
            black = (mean(black, na.rm = TRUE) * 100),
            asian = (mean(asian, na.rm = TRUE) * 100),
            multiracial = (mean(multiracial, na.rm = TRUE) * 100),
            other = (mean(other, na.rm = TRUE) * 100),
            native_american = (mean(native_american, na.rm = TRUE) * 100),
            pacific_islander = (mean(pacific_islander, na.rm = TRUE) * 100),
            hispanic_latinx = (mean(hispanic_latinx, na.rm = TRUE) * 100)) %>% 
  pivot_longer(cols = 2:9,
               names_to = "race",
               values_to = "race_percentage") %>% 
  mutate(race = str_replace(string = race,
                            pattern = "_",
                            replacement = " "),
         race = str_to_title(race))
  
daily_cost_bin_breaks <- quantile(data_plot_race_daily_cost_bins$daily_cost_per_visitor, 
                                  prob = seq(0, 1, length = 6), type = 5)
         

## -- create plot -- ##

# parameters
racial_group_colors <- c("Other" = "#999999", "Pacific Islander" = "#E69F00", "Multiracial" = "#56B4E9",
                              "Asian" = "#009E73", "Black" = "#F0E442", "White" = "#0072B2", 
                              "Native American" = "#D55E00", "Hispanic Latinx" = "#CC79A7")

# plot for shiny
plot_race_daily_cost <- ggplot(data = data_plot_race_daily_cost) +
  geom_col(aes(x = factor(daily_cost_per_visitor_bins),
               y = race_percentage,
               fill = reorder(race, race_percentage)),
           stat = "identity",
           position = "dodge") +
  coord_flip() +
  scale_fill_manual(values = racial_group_colors) +
  scale_x_discrete(labels = c("1" = "$0 - $2.90", "2" = "$2.90 - $5", "3" = "$5 - $7.20", 
                              "4" = "$7.20 - $13", "5" = "$13 - $279"), 
                   breaks = c("1", "2", "3", "4", "5")) +
  geom_vline(xintercept = c(0.5, 1.5, 2.5, 3.5, 4.5), 
             color = "lightgrey") +
  labs(x = "Daily cost per visitor ($)",
       y = "Percentage (%)",
       title = "Breakdown of Race of Home ZIP Codes vs. Daily Cost per Visitor",
       subtitle = "for Overnight Reservations in California",
       fill = "Race") +
  theme_minimal() +
  theme(plot.background = element_rect("white"),
        panel.grid.major.x = element_blank()
        # ## only needed for saving as image
        # axis.text = element_text(size = 20),
        # axis.title = element_text(size = 22, face = "bold"),
        # title = element_text(size = 24, face = "bold")
        )

plot_race_daily_cost
```

#### Race x daily cost (Option 2)

```{r}

```


#### Race x length of stay (Option 1)

```{r}
## -- data wrangle -- ##
data_plot_race_length_of_stay_bins <- data_ridb_acs_2018 %>% 
  select(agency, regional_area, park, customer_zip, asian, black, hispanic_latinx, 
         multiracial, native_american, other, pacific_islander, white,
         length_of_stay) %>% 
  mutate(length_of_stay_bins = ntile(length_of_stay, 5)) 

data_plot_race_length_of_stay <- data_plot_race_length_of_stay_bins %>% 
  group_by(length_of_stay_bins) %>% 
  summarize(white = (mean(white, na.rm = TRUE) * 100),
            black = (mean(black, na.rm = TRUE) * 100),
            asian = (mean(asian, na.rm = TRUE) * 100),
            multiracial = (mean(multiracial, na.rm = TRUE) * 100),
            other = (mean(other, na.rm = TRUE) * 100),
            native_american = (mean(native_american, na.rm = TRUE) * 100),
            pacific_islander = (mean(pacific_islander, na.rm = TRUE) * 100),
            hispanic_latinx = (mean(hispanic_latinx, na.rm = TRUE) * 100)) %>% 
  pivot_longer(cols = 2:9,
               names_to = "race",
               values_to = "race_percentage") %>% 
  mutate(race = str_replace(string = race,
                            pattern = "_",
                            replacement = " "),
         race = str_to_title(race))
  
length_of_stay_bin_breaks <- quantile(data_plot_race_length_of_stay_bins$length_of_stay, 
                                      prob = seq(0, 1, length = 6), type = 5)
         

## -- create plot -- ##

# parameters
racial_group_colors <- c("Other" = "#999999", "Pacific Islander" = "#E69F00", "Multiracial" = "#56B4E9",
                              "Asian" = "#009E73", "Black" = "#F0E442", "White" = "#0072B2", 
                              "Native American" = "#D55E00", "Hispanic Latinx" = "#CC79A7")

# plot for shiny
plot_race_length_of_stay <- ggplot(data = data_plot_race_length_of_stay) +
  geom_col(aes(x = factor(length_of_stay_bins),
               y = race_percentage,
               fill = reorder(race, race_percentage)),
           stat = "identity",
           position = "dodge") +
  coord_flip() +
  scale_fill_manual(values = racial_group_colors) +
  scale_x_discrete(labels = c("1" = "1 \nday", "2" = "1 - 2 \ndays", "3" = "2 \ndays", 
                              "4" = "2 -3 \ndays", "5" = "3 - 22 \ndays"), 
                   breaks = c("1", "2", "3", "4", "5")) +
  geom_vline(xintercept = c(0.5, 1.5, 2.5, 3.5, 4.5), 
             color = "lightgrey") +
  labs(x = "Length of Stay",
       y = "Percentage (%)",
       title = "Breakdown of Race of Home ZIP Codes vs. Length of Stay",
       subtitle = "for Overnight Reservations in California",
       fill = "Race") +
  theme_minimal() +
  theme(plot.background = element_rect("white"),
        panel.grid.major.x = element_blank()
        # ## only needed for saving as image
        # axis.text = element_text(size = 20),
        # axis.title = element_text(size = 22, face = "bold"),
        # title = element_text(size = 24, face = "bold")
        )

plot_race_length_of_stay
```

#### Race x length of stay (Option 2)

```{r}

```


#### Education x distance traveled (Option 1)

```{r}
## -- data wrangle -- ##
data_plot_education_distance_traveled_bins <- data_ridb_acs_2018 %>% 
  select(agency, regional_area, park, customer_zip, college, hs_GED_or_below, 
         master_or_above, some_college, distance_traveled_m) %>% 
  mutate(distance_traveled_mi = distance_traveled_m * 0.000621371) %>% 
  drop_na(distance_traveled_mi) %>% 
  mutate(distance_traveled_bins = ntile(distance_traveled_mi, 5)) 

data_plot_education_distance_traveled <- data_plot_education_distance_traveled_bins %>% 
  group_by(distance_traveled_bins) %>% 
  summarize(college = (mean(college, na.rm = TRUE) * 100),
            hs_GED_or_below = (mean(hs_GED_or_below, na.rm = TRUE) * 100),
            master_or_above = (mean(master_or_above, na.rm = TRUE) * 100),
            some_college = (mean(some_college, na.rm = TRUE) * 100)) %>% 
  pivot_longer(cols = 2:5,
               names_to = "education",
               values_to = "education_percentage") %>% 
  mutate(education = factor(education, 
                               levels = c("hs_GED_or_below", "some_college",
                                          "college", "master_or_above")),
         education = str_replace(string = education,
                            pattern = "hs_GED_or_below",
                            replacement = "High school, GED, or below"),
         education = str_replace(string = education,
                            pattern = "some_college",
                            replacement = "Some College"),
         education = str_replace(string = education,
                            pattern = "college",
                            replacement = "Associates or bachelors degree"),
         education = str_replace(string = education,
                            pattern = "master_or_above",
                            replacement = "Masters degree or higher"))
  
distance_traveled_bin_breaks <- quantile(data_plot_race_distance_traveled_bins$distance_traveled_mi, 
                                         prob = seq(0, 1, length = 6), type = 5)
         

## -- create plot -- ##

# parameters

# plot for shiny
plot_education_distance_traveled <- ggplot(data = data_plot_education_distance_traveled) +
  geom_col(aes(x = factor(distance_traveled_bins),
               y = education_percentage,
               fill = reorder(education, education_percentage)),
           stat = "identity",
           position = "dodge") +
  coord_flip() +
  scale_fill_viridis_d() +
  scale_x_discrete(labels = c("1" = "0 - 60.2", "2" = "60.2 - 116.9", "3" = "116.9 - 180.9", 
                              "4" = "180.9 - \n299.3", "5" = "299.3 - \n3,613.7"), 
                   breaks = c("1", "2", "3", "4", "5")) +
  geom_vline(xintercept = c(0.5, 1.5, 2.5, 3.5, 4.5), 
             color = "lightgrey") +
  labs(x = "Distance Traveled (miles)",
       y = "Percentage (%)",
       title = "Breakdown of Levels of Education in Home ZIP Codes vs. Distance Traveled",
       subtitle = "for Overnight Reservations in California",
       fill = "Education") +
  theme_minimal() +
  theme(plot.background = element_rect("white"),
        panel.grid.major.x = element_blank()
        # ## only needed for saving as image
        # axis.text = element_text(size = 20),
        # axis.title = element_text(size = 22, face = "bold"),
        # title = element_text(size = 24, face = "bold")
        )

plot_education_distance_traveled
```

#### Education x distance traveled (Option 2)

```{r}

```


#### Education x site type (Option 1)

```{r}
## -- data wrangle -- ##
data_plot_education_site_type <- data_ridb_acs_2018 %>% 
  select(agency, regional_area, park, customer_zip, college, hs_GED_or_below, 
         master_or_above, some_college, aggregated_site_type) %>% 
  group_by(aggregated_site_type) %>% 
  summarize(college = (mean(college, na.rm = TRUE) * 100),
            hs_GED_or_below = (mean(hs_GED_or_below, na.rm = TRUE) * 100),
            master_or_above = (mean(master_or_above, na.rm = TRUE) * 100),
            some_college = (mean(some_college, na.rm = TRUE) * 100)) %>% 
  pivot_longer(cols = 2:5,
               names_to = "education",
               values_to = "education_percentage") %>% 
  mutate(education = factor(education, 
                               levels = c("hs_GED_or_below", "some_college",
                                          "college", "master_or_above")),
         education = str_replace(string = education,
                            pattern = "hs_GED_or_below",
                            replacement = "High school, GED, or below"),
         education = str_replace(string = education,
                            pattern = "some_college",
                            replacement = "Some College"),
         education = str_replace(string = education,
                            pattern = "college",
                            replacement = "Associates or bachelors degree"),
         education = str_replace(string = education,
                            pattern = "master_or_above",
                            replacement = "Masters degree or higher"))
         

## -- create plot -- ##

# parameters

# plot for shiny
plot_education_site_type_1 <- ggplot(data = data_plot_education_site_type) +
  geom_col(aes(x = aggregated_site_type,
               y = education_percentage,
               fill = reorder(education, education_percentage)),
           stat = "identity",
           position = "dodge") +
  coord_flip() +
  scale_fill_viridis_d() +
  geom_vline(xintercept = c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5, 6.5), 
             color = "lightgrey") +
  scale_x_discrete(limits = c("equestrian", "remote", "rv only", "rv or tent", "shelter", "tent only", "water"),
                   labels = c("Equestrian", "Remote", "RV Only", "RV or Tent", "Shelter", "Tent Only", "Water")) +
  labs(x = "Site Types",
       y = "Percentage (%)",
       fill = "Education",
       title = "Breakdown of Levels of Education in Home ZIP Codes vs. Site Type",
       subtitle = "for Overnight Reservations in California") +
  theme_minimal() +
  theme(plot.background = element_rect("white"),
        panel.grid.major.x = element_blank())
plot_education_site_type_1
```

#### Education x site type (Option 2)

```{r}

```


#### Education x booking window (Option 1)

```{r}
## -- data wrangle -- ##
data_plot_education_booking_window_bins <- data_ridb_acs_2018 %>% 
  select(agency, regional_area, park, customer_zip, college, hs_GED_or_below, 
         master_or_above, some_college, booking_window) %>% 
  mutate(booking_window_bins = ntile(booking_window, 5)) 

data_plot_education_booking_window <- data_plot_education_booking_window_bins %>% 
  group_by(booking_window_bins) %>% 
  summarize(college = (mean(college, na.rm = TRUE) * 100),
            hs_GED_or_below = (mean(hs_GED_or_below, na.rm = TRUE) * 100),
            master_or_above = (mean(master_or_above, na.rm = TRUE) * 100),
            some_college = (mean(some_college, na.rm = TRUE) * 100)) %>% 
  pivot_longer(cols = 2:5,
               names_to = "education",
               values_to = "education_percentage") %>% 
  mutate(education = factor(education, 
                               levels = c("hs_GED_or_below", "some_college",
                                          "college", "master_or_above")),
         education = str_replace(string = education,
                            pattern = "hs_GED_or_below",
                            replacement = "High school, GED, or below"),
         education = str_replace(string = education,
                            pattern = "some_college",
                            replacement = "Some College"),
         education = str_replace(string = education,
                            pattern = "college",
                            replacement = "Associates or bachelors degree"),
         education = str_replace(string = education,
                            pattern = "master_or_above",
                            replacement = "Masters degree or higher"))
  
booking_window_bin_breaks <- quantile(data_plot_education_booking_window_bins$booking_window, 
                                      prob = seq(0, 1, length = 6), type = 5)
         

## -- create plot -- ##

# parameters

# plot for shiny
plot_education_booking_window <- ggplot(data = data_plot_education_booking_window) +
  geom_col(aes(x = factor(booking_window_bins),
               y = education_percentage,
               fill = reorder(education, education_percentage)),
           stat = "identity",
           position = "dodge") +
  coord_flip() +
  scale_fill_viridis_d() +
  scale_x_discrete(labels = c("1" = "0 - 7 \n(days)", "2" = "7 - 27 \n(days)", 
                              "3" = "1 - 2.5 \n(months)", "4" = "2.5 - 4.5 \n(months)", 
                              "5" = "4.5 months - \n1.8 years"), 
                   breaks = c("1", "2", "3", "4", "5")) +
  geom_vline(xintercept = c(0.5, 1.5, 2.5, 3.5, 4.5), 
             color = "lightgrey") +
  labs(x = "Booking window",
       y = "Percentage (%)",
       title = "Breakdown of Levels of Education in Home ZIP Codes vs. Booking Window",
       subtitle = "for Overnight Reservations in California",
       fill = "Education") +
  theme_minimal() +
  theme(plot.background = element_rect("white"),
        panel.grid.major.x = element_blank()
        # ## only needed for saving as image
        # axis.text = element_text(size = 20),
        # axis.title = element_text(size = 22, face = "bold"),
        # title = element_text(size = 24, face = "bold")
        )

plot_education_booking_window
```

#### Education x booking window (Option 2)

```{r}

```


#### Education x daily cost (Option 1)

```{r}
## -- data wrangle -- ##
data_plot_education_daily_cost_bins <- data_ridb_acs_2018 %>% 
  select(agency, regional_area, park, customer_zip, college, hs_GED_or_below, 
         master_or_above, some_college, daily_cost_per_visitor) %>% 
  mutate(daily_cost_per_visitor_bins = ntile(daily_cost_per_visitor, 5)) 

data_plot_education_daily_cost <- data_plot_education_daily_cost_bins %>% 
  group_by(daily_cost_per_visitor_bins) %>% 
  summarize(college = (mean(college, na.rm = TRUE) * 100),
            hs_GED_or_below = (mean(hs_GED_or_below, na.rm = TRUE) * 100),
            master_or_above = (mean(master_or_above, na.rm = TRUE) * 100),
            some_college = (mean(some_college, na.rm = TRUE) * 100)) %>% 
  pivot_longer(cols = 2:5,
               names_to = "education",
               values_to = "education_percentage") %>% 
  mutate(education = factor(education, 
                               levels = c("hs_GED_or_below", "some_college",
                                          "college", "master_or_above")),
         education = str_replace(string = education,
                            pattern = "hs_GED_or_below",
                            replacement = "High school, GED, or below"),
         education = str_replace(string = education,
                            pattern = "some_college",
                            replacement = "Some College"),
         education = str_replace(string = education,
                            pattern = "college",
                            replacement = "Associates or bachelors degree"),
         education = str_replace(string = education,
                            pattern = "master_or_above",
                            replacement = "Masters degree or higher"))
  
daily_cost_bin_breaks <- quantile(data_plot_education_daily_cost_bins$daily_cost_per_visitor, 
                                  prob = seq(0, 1, length = 6), type = 5)
         

## -- create plot -- ##

# parameters

# plot for shiny
plot_education_daily_cost <- ggplot(data = data_plot_education_daily_cost) +
  geom_col(aes(x = factor(daily_cost_per_visitor_bins),
               y = education_percentage,
               fill = reorder(education, education_percentage)),
           stat = "identity",
           position = "dodge") +
  coord_flip() +
  scale_fill_viridis_d() +
  scale_x_discrete(labels = c("1" = "$0 - $2.90", "2" = "$2.90 - $5", "3" = "$5 - $7.20", 
                              "4" = "$7.20 - $13", "5" = "$13 - $279"), 
                   breaks = c("1", "2", "3", "4", "5")) +
  geom_vline(xintercept = c(0.5, 1.5, 2.5, 3.5, 4.5), 
             color = "lightgrey") +
  labs(x = "Daily cost per visitor ($)",
       y = "Percentage (%)",
       title = "Breakdown of Levels of Education in Home ZIP Codes vs. Daily Cost per Visitor",
       subtitle = "for Overnight Reservations in California",
       fill = "Education") +
  theme_minimal() +
  theme(plot.background = element_rect("white"),
        panel.grid.major.x = element_blank()
        # ## only needed for saving as image
        # axis.text = element_text(size = 20),
        # axis.title = element_text(size = 22, face = "bold"),
        # title = element_text(size = 24, face = "bold")
        )

plot_race_daily_cost
```

#### Education x daily cost (Option 2)

```{r}

```


#### Education x length of stay (Option 1)

```{r}
## -- data wrangle -- ##
data_plot_education_length_of_stay_bins <- data_ridb_acs_2018 %>% 
  select(agency, regional_area, park, customer_zip, college, hs_GED_or_below, 
         master_or_above, some_college, length_of_stay) %>% 
  mutate(length_of_stay_bins = ntile(length_of_stay, 5)) 

data_plot_education_length_of_stay <- data_plot_education_length_of_stay_bins %>% 
  group_by(length_of_stay_bins) %>% 
  summarize(college = (mean(college, na.rm = TRUE) * 100),
            hs_GED_or_below = (mean(hs_GED_or_below, na.rm = TRUE) * 100),
            master_or_above = (mean(master_or_above, na.rm = TRUE) * 100),
            some_college = (mean(some_college, na.rm = TRUE) * 100)) %>% 
  pivot_longer(cols = 2:5,
               names_to = "education",
               values_to = "education_percentage") %>% 
  mutate(education = factor(education, 
                               levels = c("hs_GED_or_below", "some_college",
                                          "college", "master_or_above")),
         education = str_replace(string = education,
                            pattern = "hs_GED_or_below",
                            replacement = "High school, GED, or below"),
         education = str_replace(string = education,
                            pattern = "some_college",
                            replacement = "Some College"),
         education = str_replace(string = education,
                            pattern = "college",
                            replacement = "Associates or bachelors degree"),
         education = str_replace(string = education,
                            pattern = "master_or_above",
                            replacement = "Masters degree or higher"))
  
length_of_stay_bin_breaks <- quantile(data_plot_education_length_of_stay_bins$length_of_stay, 
                                      prob = seq(0, 1, length = 6), type = 5)
         

## -- create plot -- ##

# parameters

# plot for shiny
plot_education_length_of_stay <- ggplot(data = data_plot_education_length_of_stay) +
  geom_col(aes(x = factor(length_of_stay_bins),
               y = education_percentage,
               fill = reorder(education, education_percentage)),
           stat = "identity",
           position = "dodge")  +
  scale_fill_viridis_d() +
  scale_x_discrete(labels = c("1" = "1 \nday", "2" = "1 - 2 \ndays", "3" = "2 \ndays", 
                              "4" = "2 -3 \ndays", "5" = "3 - 22 \ndays"), 
                   breaks = c("1", "2", "3", "4", "5")) +
  geom_vline(xintercept = c(0.5, 1.5, 2.5, 3.5, 4.5), 
             color = "lightgrey") +
  labs(x = "Length of Stay",
       y = "Percentage (%)",
       title = "Breakdown of Levels of Education in Home ZIP Codes vs. Length of Stay",
       subtitle = "for Overnight Reservations in California",
       fill = "Education") +
  theme_minimal() +
  theme(plot.background = element_rect("white"),
        panel.grid.major.x = element_blank()
        # ## only needed for saving as image
        # axis.text = element_text(size = 20),
        # axis.title = element_text(size = 22, face = "bold"),
        # title = element_text(size = 24, face = "bold")
        )

plot_education_length_of_stay
```

#### Education x length of stay (Option 2)

```{r}

```



#### Language 

Similar graphs to those above would exist for:

* Language x distance traveled
* Language x site type
* Language x booking window
* Language x daily cost
* Language x length of stay


#### Median-income x distance traveled

Similar graphs to those above would exist for:

* Median-income x distance traveled
* Median-income x site type
* Median-income x booking window
* Median-income x daily cost
* Median-income x length of stay


#### Booking window x site type

```{r}
## -- data wrangle -- ##
data_plot_booking_window_site_type <- data_ridb_acs_2018 %>% 
  #select(agency, regional_area, park, booking_window, aggregated_site_type) %>% 
  group_by(aggregated_site_type) %>% 
  summarise(mean_booking_window = mean(booking_window, na.rm = TRUE)) %>% 
  mutate(aggregated_site_type = str_to_title(aggregated_site_type))

## -- create plot -- ##

# parameters

# plot for shiny
plot_booking_window_site_type <- ggplot(data = data_plot_booking_window_site_type) +
  geom_col(aes(y = reorder(aggregated_site_type, mean_booking_window),
           x = mean_booking_window), fill = "#009900FF") +
  labs(x = "Booking Window (days)",
       y = "",
       title = "Booking Window vs. Distance Traveled",
       subtitle = "for Overnight Reservations in California") +
  theme_minimal() +
  theme(plot.background = element_rect("white"),
        panel.grid.major.x = element_blank(),
        # ## only needed for saving as image
        # axis.text = element_text(size = 20),
        # axis.title = element_text(size = 22, face = "bold"),
        # title = element_text(size = 24, face = "bold")
        )

plot_booking_window_site_type
```


#### Booking window x distance traveled
Similar graphs to those above would exist for booking window x distance traveled

## Save plot all data to RDS

```{r, eval=FALSE}
plot_data <- c("data_plot_race_distance_traveled", "data_plot_race_site_type", 
               "data_plot_race_booking_window", "data_plot_race_daily_cost", 
               "data_plot_race_length_of_stay", "data_plot_education_distance_traveled", 
               "data_plot_education_site_type", "data_plot_education_booking_window", 
               "data_plot_education_daily_cost", "data_plot_education_length_of_stay", 
               "data_plot_booking_window_site_type")

for (i in seq_along(plot_data)){
  saveRDS(object = get(plot_data[[i]]),
          file = paste0("../../../../data_clean/2018_data_graphs_comparison_variables/2018_", 
                        plot_data[[i]],
                        ".rds"))
}
```


