---
title: "Data Viz for Shiny App"
author: "Clarissa"
date: "3/17/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)
library(lubridate)
library(sf)
library(tidycensus)
library(patchwork)
library(scales)
library(tmap)
library(vroom)
library(paletteer)

options(scipen = 999)

# load script to pull and clean ACS data
source("../functions/function_acs_race.R")
source("../functions/function_acs_median_income.R")
source("../functions/function_acs_transportation.R")
source("../functions/function_acs_education.R")
source("../functions/function_acs_language.R")
```

# Read in data

```{r, message=FALSE, warning=FALSE}
# read in joined data
data_ridb_acs_2018 <- vroom(file = "../../../../data_clean/2018_joined_data.csv",
                            delim = ",") ## non-map graphs (no geometries)
# data_ridb_acs_2018 <- readRDS(file = "../../../../data_clean/2018_joined_data.rds") ## maps (don't use RDS for non-map viz, too slow)

# ACS CA data
acs_subset_calculate_race(geography = "zcta", year = 2018, state = "California")
acs_subset_calculate_education(geography = "zcta", year = 2018, state = "California")
acs_subset_calculate_language(geography = "zcta", state = "California")
acs_subset_calculate_transportation(geography = "zcta", year = 2018, state = "California")
acs_subset_calculate_median_income(geography = "zcta", year = 2018, state = "California")

# ACS US data
# acs_subset_calculate_race(geography = "zcta", year = 2018, state = NULL)
# acs_subset_calculate_education(geography = "zcta", year = 2018, state = NULL)
```


# Graphs

## Race x distance traveled

```{r}
## -- data wrangle -- ##
data_plot_race_distance_traveled_bins <- data_ridb_acs_2018 %>% 
  select(agency, regional_area, park, customer_zip, asian, black, hispanic_latinx, 
         multiracial, native_american, other, pacific_islander, white,
         distance_traveled_m) %>% 
  mutate(distance_traveled_mi = distance_traveled_m * 0.000621371) %>% 
  drop_na(distance_traveled_mi) %>% 
  mutate(distance_traveled_bins = ntile(distance_traveled_mi, 5)) 

data_plot_race_distance_traveled <- data_plot_race_distance_traveled_bins %>% 
  group_by(distance_traveled_bins) %>% 
  summarize(white = (mean(white, na.rm = TRUE) * 100),
            black = (mean(black, na.rm = TRUE) * 100),
            asian = (mean(asian, na.rm = TRUE) * 100),
            multiracial = (mean(multiracial, na.rm = TRUE) * 100),
            other = (mean(other, na.rm = TRUE) * 100),
            native_american = (mean(native_american, na.rm = TRUE) * 100),
            pacific_islander = (mean(pacific_islander, na.rm = TRUE) * 100),
            hispanic_latinx = (mean(hispanic_latinx, na.rm = TRUE) * 100)) %>% 
  pivot_longer(cols = 2:9,
               names_to = "race",
               values_to = "race_percentage") %>% 
  mutate(race = str_replace(string = race,
                            pattern = "_",
                            replacement = " "),
         race = str_to_title(race))
  
distance_traveled_bin_breaks <- quantile(data_plot_race_distance_traveled_bins$distance_traveled_mi, prob = seq(0, 1, length = 6), type = 5)
         

## -- create plot -- ##

# parameters
racial_group_colors <- c("Other" = "#999999", "Pacific Islander" = "#E69F00", "Multiracial" = "#56B4E9",
                              "Asian" = "#009E73", "Black" = "#F0E442", "White" = "#0072B2", 
                              "Native American" = "#D55E00", "Hispanic Latinx" = "#CC79A7")

# plot for shiny
plot_race_distance_traveled <- ggplot(data = data_plot_race_distance_traveled) +
  geom_col(aes(x = distance_traveled_bins,
               y = race_percentage,
               fill = race),
           stat = "identity",
           position = "dodge")  +
  scale_fill_manual(values = racial_group_colors) +
  labs(x = "Distance Traveled (miles)",
       y = "Percentage (%)",
       title = "Breakdown of Education Levels of ZIP Codes in 2018",
       subtitle = "Visitors' home ZIP codes for Overnight Reservations in California \nvs. California Residents") +
  #scale_x_discrete(labels = c("1" = "1st", "2" = "2nd", "3" = "3rd", "4" = "4th", "5" = "5th")) +
  theme_minimal() +
  theme(plot.background = element_rect("white"),
        panel.grid.major.y = element_blank(),
        # ## only needed for saving as image
        # axis.text = element_text(size = 20),
        # axis.title = element_text(size = 22, face = "bold"),
        # title = element_text(size = 24, face = "bold")
        )

plot_race_distance_traveled
```




## Race x site type

```{r}
## -- data wrangle -- ##


## -- create plot -- ##

# parameters

# plot for shiny
```


## Race x booking window

## Race x daily cost

## Race x length of stay


## Education x distance traveled

## Education x site type

## Education x booking window

## Education x daily cost

## Education x length of stay


## Transportation x distance traveled

## Transportation x site type

## Transportation x booking window

## Transportation x daily cost

## Transportation x length of stay


## Language x distance traveled

## Language x site type

## Language x booking window

## Language x daily cost

## Language x length of stay


## Median-income x distance traveled

## Median-income x site type

## Median-income x booking window

## Median-income x daily cost

## Median-income x length of stay


## Booking window x site type

```{r}
## -- data wrangle -- ##
data_plot_booking_window_site_type <- data_ridb_acs_2018 %>% 
  #select(agency, regional_area, park, booking_window, aggregated_site_type) %>% 
  group_by(aggregated_site_type) %>% 
  summarise(mean_booking_window = mean(booking_window, na.rm = TRUE))
data_plot_booking_window_site_type$aggregated_site_type <- with(data_plot_booking_window_site_type, reorder(aggregated_site_type, mean_booking_window))

## -- create plot -- ##

# parameters

# plot for shiny
plot_booking_window_site_type <- ggplot(data = data_plot_booking_window_site_type) +
  geom_col(aes(y = aggregated_site_type,
           x = mean_booking_window))

plot_booking_window_site_type

plot_booking_window_site_type2 <- ggplot(data = data_ridb_acs_2018 %>% filter(booking_window > 0)) +
  geom_boxplot(aes(x = booking_window, 
                     #y = stat(count) / sum(count),
                     fill = aggregated_site_type)) +
  facet_wrap(~aggregated_site_type)

plot_booking_window_site_type2
```


## Booking window x distance traveled

```{r}
## -- data wrangle -- ##


## -- create plot -- ##

# parameters

# plot for shiny
ggplot(data = )
```



# Save plot all data to RDS

```{r}
plot_data <- c(
  
)

for (i in seq_along(plot_data)){
  saveRDS(object = get(plot_data[[i]]),
          file = paste0("../../../../data_clean/2018_data_graphs_comparison_variable/2018_", 
                        plot_data[[i]],
                        ".rds"))
}
```


