---
title: "Data Viz: Final Project"
author: "Halina Do-Linh"
date: "3/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)
library(tidycensus)
library(tmap)
library(sf)
```


# Set up data

## Functions

```{r}
# ridb subset pre 2018
source("../analysis/functions/function_ridb_subset-pre2018.R")
# acs median income
source("../analysis/functions/function_acs_median_income.R")
# calculated variables 
source("../analysis/functions/function_ridb_variable_calculate-pre2018.R")
```

## Creating ridb, acs, and combined datasets

```{r}
# read and cleaned and subsetted ridb 2018 data using function
# data_ridb_2018
RIDB_subset_pre2018("../../data_raw/reservations2018.csv", "CA", 2018)

# read in acs median income data using function
# data_acs_2018_median_income
acs_subset_calculate_median_income(geography = "zcta",
                                   year = 2018,
                                   state = NULL) # not all CA visits are from CA

# add calculated variables
# output name needs to be in quotes
RIDB_calculate_pre2018(input_df_name = data_ridb_2018, 
                       output_df_name = "data_ridb_calculated_2018")

# combined data
data_combined_2018 <- left_join(data_ridb_calculated_2018, 
                                data_acs_2018_median_income, 
                                by = c("customer_zip" = "zip_code"))

## cleaning combined data ##
# FIX SEQUOIA HERE
data_clean_combined_2018 <- data_combined_2018 %>% 
  group_by(park, regional_area, agency) %>%
  # add median income stats
  summarize(median_median_income = median(median_income, na.rm = TRUE),
            mean_median_income = round(mean(median_income, na.rm = TRUE), 0),
            max_median_income = max(median_income, na.rm = TRUE),
            min_median_income = min(median_income, na.rm = TRUE),
            facility_latitude = mean(facility_latitude),
            facility_longitude = mean(facility_longitude),
            count = n()) %>%
  # create geometry column
  st_as_sf(coords = c("facility_longitude","facility_latitude"), crs = 4326) %>%
  ## cleaning up park ##
  mutate(park = str_replace(string = park,
                            pattern = "PYRAMID LAKE / LOS ALAMOS CAMPGROUND",
                            replacement = "PYRAMID LAKE LOS ALAMOS CAMPGROUND")) %>%
  mutate(park = str_replace(string = park,
                            pattern = "Lewis @ French Meadows",
                            replacement = "Lewis at French Meadows")) %>% 
  mutate(park = str_replace(string = park,
                            pattern = "Cg",
                            replacement = "Campground")) %>% 
  mutate(park = str_remove_all(string = park,
                               pattern = paste(c("\\(.*",
                                                 "---.*",
                                                 ",.*",
                                                 "[:digit:]{2,}.*"),
                                               collapse = "|"))) %>%
  mutate(park = str_to_title(park)) %>% 
  # remove sites not in CA
  filter(park != "Blue Lake Campground",
         park != "Bear Lake Campground ")
```

## median income for regional area and agency subset
```{r}
# cleaning
data_regional_combined_2018 <- data_combined_2018 %>%
  mutate(regional_area = str_replace(string = regional_area,
                                     pattern = "Sequoia & Kings Canyon National Parks", # NEED TO FIGURE OUT HOW TO FIND PATTERN WITH ONE S
                                     replacement = "Sequoia & Kings Canyon National Park")) %>% 
  group_by(regional_area, agency) %>%
  # add median income stats
  summarize(mean_median_income = round(mean(median_income, na.rm = TRUE), 0),
            facility_latitude = mean(facility_latitude),
            facility_longitude = mean(facility_longitude),
            count = n()) %>%
  # create geometry column
  st_as_sf(coords = c("facility_longitude","facility_latitude"), crs = 4326)
```


## CA geometry from ACS
```{r}
# pull in acs CA data
ca_geom <- get_acs(geography = "state", year = 2018, geometry = TRUE, 
                             state = "California",
                             summary_var = "B01001_001", # dummy var
                             variables = c(male = "B01001_002")) %>% # dummy var
  # select for only zip (NAME) and geometry
  select(NAME, geometry)
```

## Save `data_clean_combined_2018` as a RDS
```{r}
saveRDS(data_clean_combined_2018, "/capstone/outdoorequity/halina/outdoor-equity/shiny/outdoor-equity-app/data_combined_CAmap_2018.rds")
```

## Save `ca_geom` as a RDS
```{r}
saveRDS(ca_geom, "/capstone/outdoorequity/halina/outdoor-equity/shiny/outdoor-equity-app/data_ca_geom.rds")
```

## Save `data_regional_combined_2018` as a RDS
```{r}
saveRDS(data_regional_combined_2018, "/capstone/outdoorequity/halina/outdoor-equity/shiny/outdoor-equity-app/data_regional_combined_2018.rds")
```


# Map

## histogram of median median income
```{r}
ggplot(data = data_clean_combined_2018, aes(x = median_median_income)) +
  geom_histogram()
```

## histogram of mean median income
```{r}
ggplot(data = data_clean_combined_2018, aes(x = mean_median_income)) +
  geom_histogram()
```

## map of median income for regional area and agencies
```{r, fig.width=8, fig.height=4}
tmap_mode("plot")
regional_tmap <- tm_shape(ca_geom) +
  tm_polygons(col = "white") +
tm_shape(data_regional_combined_2018) +
  tm_symbols(shape = "agency",
             title.shape = "Agency",
             title.col = "Estimated Household Income \nof Visitor ZIP Code",
             col = "mean_median_income",
             size = 0.3,
             breaks = c(50000, 60000, 70000, 80000, 90000, 110000),
             palette = "viridis",
             legend.hist = TRUE) +
  tm_legend(outside = TRUE,
            legend.outside.position = "right") +
  tm_layout(main.title = "Estimated Household Income at \nOvernight Reservations for California (2018)")
# tm_shape(data_regional_combined_2018 %>% filter(count > 25172)) +
#   tm_text("regional_area",
#           size = 0.48,
#           fontfamily = "Kefa", 
#           fontface = "bold",
#           along.lines = T)

# tm_layout(basemaps = leaflet::providers$OpenStreetMap)
  # tm_text("regional_area", 
  #         size = 0.3)
tmap_save(regional_tmap, "regional.png")
regional_tmap
```


## map of median median income at park sites
```{r}
# add explanatory text about median household income for US
tmap_mode("view") # vs plot
tm_shape(ca_geom) +
  # this layer doesn't need to be interactive and this removes the popup vars
  tm_polygons(interactive = FALSE) + 
tm_shape(data_clean_combined_2018) +
  tm_view(view.legend.position = c("bottom", "right")) + # doesn't work for interactive maps??
  tm_symbols(size = "count",
             col = "mean_median_income",
             alpha = 0.8,
             title.col = "Estimated Household Income of Visitor ZIP Code",
             style = "jenks",
             palette = "viridis",
             popup.vars = c("Agency" = "agency",
                            "Number of Reservations" = "count", 
                            "Estimated Household Income" = "mean_median_income"))
             # legend.hist = TRUE) can't use histogram for interactive map?
```



# OLD

```{r}
## OLD CODE ##
  # tm_shape(shapefile_with_MNO_data) + 
  # tm_dots("MNO_variable")
  # tm_fill(col = "number_reservations",
  #         palette = "PuRd",
  #         style = "jenks",
  #         n = 10)
  # tm_layout(title = "Median Income of Visitors' Home ZIP at Reservable Sites in CA",
  #           legend.position = c("left", "bottom"))
             # breaks = c(40000, 50000, 60000, 70000, 80000, 90000, 100000, 150000, 200000),


# load data
# data_combined_2018 <- read.csv("../../../data_clean/2018_joined_data.csv")

## OLD CODE ## 
#                                pattern = paste(c("\\(CA\\) --- .*",
#                                                  "\\(CA\\)-*"
#                                                  #"\\(*",
#                                                  "--- .*"),
#                                                collapse = "|")))
# 
# 
# pattern = paste(c("---", "\\(CA\\)", "-"), collapse = "|")))
# (CA) --- FPIN2377
# \\(CA\\) --- \W
# --- 12390100
# (CA)

# # add regional_area
# data_combined_2018 <- data_combined_2018 %>% 
#   mutate(regional_area = case_when(agency == "USFS" ~ parent_location,
#                                    agency %in% c("NPS", "BOR", "USACE") ~ region_description)) %>% mutate(regional_area = str_replace(string = regional_area,
#                                          pattern = paste(c("NF - FS", "NF -FS", "NF- FS",
#                                                            "NF-FS", "-FS", " - FS"), 
#                                                          collapse = "|"),
#                                          replacement = "National Forest")) %>% 
#   mutate(regional_area = str_to_title(regional_area))

# add calculated variables 
#RIDB_calculate_pre2018(data_ridb_2018, output_df_name = "data_test_calculated_2018")
# Error in paste(output_df_name) : object 'data_combined_calculated_2018' not found
# RIDB_calculate_pre2018(data_combined_2018, data_combined_2018_clean)
# Error in assign(paste(output_df_name), data.frame(df), envir = .GlobalEnv) : variable names are limited to 10000 bytes
```