---
title: "About Page"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## What is outdoor recreation and why does it matter?

Access to nature and other outdoor recreation are important for both physical and mental health. In the United States, there are many levels of government that manage public land, including local, state, and federal agencies. Federal public lands specifically play an important role in providing access to outdoor recreation across the country. Many studies have shown that federally managed public land is accessed unequally due to historic and current problems. However, there is a lack of strong data-driven analytical tools to understand the specifics of how this unequal access currently manifests. In order for decision makers to take mitigating steps to create more equitable access, they must be able to visualize how recreational opportunities on federal public lands are currently being accessed on both a country- or state-wide and also a park- or region-specific scale.

Our overarching objective for this project is to utilize data from the [Recreation Information Database (RIDB)](https://ridb.recreation.gov/landing) and the [U.S. Census Bureau](https://data.census.gov/cedsci/table?q=United%20States) to analyze spatial and temporal trends in access and demand of federal recreation users. This analysis will explore park and regional demand as well as trends among different socioeconomic groups such as distance traveled, nights stayed, cost, site type, and more.


## What is Environmental Justice?

```{r}
print("testing")
```



## User Guide