---
title: "About Page"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(tmap)
library(plotly)
library(vroom)
library(scales)

# read in necessary data
data_joined_2018 <- readRDS("../data/2018_joined_data.rds")
acs_ca_2018 <- readRDS("../data/2018_ca_acs_all.rds")

# source functions for plots
source("../r/relationship_plots/median_income_deciles.R")
source("../r/relationship_plots/race_top_quartile.R")
source("r/not_reactive_booking_window_plot.R")
source("r/not_reactive_median_income_dist_travel_data.R")
source("r/not_reactive_median_income_dist_travel_plot.R")
source("r/not_reactive_race_dist_travel_data.R")
source("r/not_reactive_race_dist_travel_plot.R")
```


## What is outdoor recreation and why does it matter?

Access to nature and other outdoor recreation have well-documented positive impacts on mental physical well-being. In the United States, there are many levels of government that manage public land, including local, state, and federal agencies. Federal public land management agencies in the United States offer a wide variety of activities to visitors, such as picnicking in parks, hiking trails, tours, campsites, and more. However, people from different socioeconomic and identity groups access federal public lands unequally due to historical discrimination and current inequities. The multi-agency program, Recreation One Stop (R1S), oversees the operations of Recreation.gov and aims to increase access to recreation by providing online resources about nationwide recreational opportunities, allowing visitors to make reservations, and making the associated data accessible to all. The rich data on visitors that R1S collects presents an opportunity for the creation of more robust data-driven analytical tools to understand the patterns and correlations of this unequal access across the country and within individual recreation areas. Decision-makers can use these tools to explore and visualize how recreational opportunities on federal public lands are accessed. 


## What is the Outdoor Equity App?

This website is an interactive visualization tool that allows users to  analyze patterns in the access and demand of visitors at reservable overnight reservable sites (such as campgrounds, cabins, hike-in, and more), using data from the [Recreation Information Database (RIDB)](https://ridb.recreation.gov/landing) and the [United States Census Bureau](https://data.census.gov/cedsci/table?q=United%20States). The analyses in this app will allow federal public land managers, researchers, nonprofit organizations, and recreation users to explore relationships among attributes of recreation opportunities, reservation practices, and socioeconomic data from the regions of visitor origin. 



## Examples of how to use the Outdoor Equity App

### Where are visitors to two campsites near each other coming from?

Federal public land managers and others may be interested in where visitors from 

```{r}

```


### How far are people of different incomes traveling ot get to two campsites near each other?

```{r}

```


### How far are different racial groups traveling to get to get to a specific campsite?

```{r}

```


### When do I need to make my reservation for visiting a specific campsite?

Both land managers and recreation users might be interested in how far in advance sites typically are booked for a specific campsite. To do this, users will navigate to the "Data Summary" tab in the navigation bar. There they can choose the "Booking Window" option from the drop-down menu, and select their site of interest. Here we want to know how far in advance sites at Upper Pines, Yosemite National Park are reserved.

```{r}
booking_window_plot(admin_unit = "Yosemite National Park", site = "Upper Pines")
```

In looking at the plot above, we can see that there is an increase in the number of reservations made between about 125 and 150 days in advance (or 4 months out).


## Learn more

For a more in-depth technical documentation of this app, please visit:


