---
title: "RIDB data cleaning explore"
author: "Clarissa Boyajian"
date: "2/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)
library(lubridate)
library(sf)
library(tidycensus)
library(patchwork)
library(scales)
library(tmap)

options(scipen = 999)


# RIDB functions
# raw data
source("functions/function_ridb_subset-pre2018.R")
source("functions/function_ridb_subset-post2019.R")
# calculate variables
source("functions/function_ridb_variable_calculate-pre2018.R")
# standardize values
# need to make function still
```


# RIDB

## Read in data, calculate varibales, standardize values

```{r}
## 2018
# read in data
RIDB_subset_pre2018(full_file_path = "../../data_raw/reservations2018.csv", 
                      state_abbrev = "CA", year = 2018)
# calculate variables
RIDB_calculate_pre2018(input_df_name = data_ridb_2018, output_df_name = "data_ridb_2018")
## create function to standardize values (or add to calculate function)
```


*Issues to consider*: 
- length of stay goes to -126
- highest price / person is $279 for a group campsite (the site isn't that expensive)


*Notes on standardizations to consider*:
- region description: 
    - change "-FS" and "- FS" to "Forest Service"
    - add indicator to regions without (i.e. not USFS or NPS)
- parent location:
    - change "-FS" and "- FS" to "Forest Service"
    - change "NF" to "National Forest"
    - change "PWR" to "Pacific West Region"
- park:
    - remove "--- #idcodehere#", and " (CA)" from ends of park names
    - fix anomolies that don't follow pattern (i.e. "region / campground name" or "campground name, region")
    - remove all uppercase
- facility zip:
    - remove everything after 5th digit
- start date:
    - min: 2017-06-19
    - max: 2019-09-30
- end date:
    - min: 2017-06-22
    - max: 2019-10-14
- order date: **the data is split by fiscal year of order date!!**
    - min: 2017-10-01
    - max: 2018-09-30

NAs:
    - facility zip: 108309
