---
title: "Data Cleaning"
author: "Clarissa Boyajian and Halina Do-Linh"
date: "1/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)
library(tidycensus)

# file path from .Rproj to outdoorequity shared folder
outdoorequity_folder_file_path <- here::here("../../../../capstone/outdoorequity/")
```

# Bring in RIDB Data

## RIDB Subsetting Function

read in functions created in R script
```{r}
source("../r/functions/function_data-subsetting-pre2018.R")
source("../r/functions/function_data-subsetting-post2019.R")
```

```{r}
# 2018
RIDB_cleaning_pre2018(full_file_path = paste0(outdoorequity_folder_file_path, "data/reservations2018.csv"), 
                      state_abbrev = "CA", df_name = "ridb_2018")
```

## Standardizing values

Notes on standardizations to consider:
- region description: 
    - change "-FS" and "- FS" to "Forest Service"
    - add indicator to regions without (i.e. not USFS or NPS)
- parent location:
    - change "-FS" and "- FS" to "Forest Service"
    - change "NF" to "National Forest"
    - change "PWR" to "Pacific West Region"
- park:
    - remove "--- #idcodehere#", and " (CA)" from ends of park names
    - fix anomolies that don't follow pattern (i.e. "region / campground name" or "campground name, region")
    - remove all uppercase
- facility zip:
    - remove everything after 5th digit
    - 108309 NAs
- start date:
    - min: 2017-06-19
    - max: 2019-09-30
- end date:
    - min: 2017-06-22
    - max: 2019-10-14
- order date: **the data is split by fiscal year of order date!!**
    - min: 2017-10-01
    - max: 2018-09-30

```{r}

```


# Bring in Census Data

```{r}

census_api_key()
```




