---
title: "Metadata exploration"
author: "Halina Do-Linh"
date: "1/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
```

# Read in data

```{r}
fp = here::here("data/FY20-historical-reservations-full.csv")

RIDB_cleaning_post2019(full_file_path = fp, 
                       state = "California", 
                       df_name = "RIDB_CA_2020")
```

# Save clean data 

```{r}
write_csv(RIDB_CA_2020, here("data/clean/RIDB_CA_2020.csv"))
```

# Metadata

```{r}
summary(RIDB_CA_2020)
```
```{r}
unique(RIDB_CA_2020$parentlocationid)
```

# Checking for NA's 

NO NAs's

- historicalreservationid
- ordernumber
- agency
- orgid
- parentlocationid
- parentlocation
- sitetype
- usetype
- productid
- inventorytype
- facilityid
- facilityzip
- facilitystate
- facilitylongitude
- facilitylatitude
- customerzip
- totalbeforetax
- discount
- totalpaid
- startdate
- enddate
- orderdate
- numberofpeople

YES NA's

- regioncode (653)
- regiondescription (653)

```{r}
# for(i in 1:ncol(RIDB_CA_2020)) {
#   sum(is.na(RIDB_CA_2020$i)) 
# }
```




